\documentclass{article}
\usepackage[utf8]{inputenc}

\title{PS5}
\author{Travis Richardson }
\date{February 2019}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Problem 3: No API}
The data I used for this problem set was an ESPN article about my favoirte soccer player, Zlatan Ibrahimovic. The article is about 35 of his best quotes; if you know about Zlatan, you know he says wild stuff. To be honest, this data will not help me with my project or in the future. I used this data because it was easily accessible. At first I wanted to use data from WhoScored.com or the Premier League website to look at all the scores from this season of the EPL. However, when using SelectorGadget and highlighting the pieces of data I would need, the CSS code that was given never gave any output in R. For my project idea, this is for sure something I will need help with. I used the tutorial (Trump Lies) you should in class to help remember how to extract the data. I did not parse the data as much as the example, however, this data was rather clean from the start. And I was not sure how to make the data into a dataframe or CSV file. I'm sure that is a simple step, but I was lost.



\section{Problem 4: API}
For this question I looked for a couple hours to find a soccer API that would work for me. The ones I could find enough information on would not let me install to R, saying the version would not work. So, eventually, I decided I would look into financial data. I uses the package "quantmod". This package allowed me to load in data from any company if I could get their symbol from Yahoo Finance. Then I was able to look at all the stock prices and chart the history of those numbers. I know this is super basic API use, but I was just happy to finally get someting to work.  
\end{document}
